---
title: "My title"
author:
- Ben Marwick (University of Washington, University of Wollongong)
- other author
date: '`r Sys.Date()`'
output: word_document
abstract: "My abstract \n"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Heading 1

This is a template Rmd for rendering a MS Word document with custom styles, including

- line numbers for      
- Headings are bold, underline, nothing.   
- Arial Narrow 10pt for tables
- page breaks with style 'Heading 5'


Now knit this doc, and edit to update the styles in the resulting docx file. Then rename as 'template' and use this in the yml of the main Rmd:

```
output:
  word_document:
    reference_docx: templates/template.docx
```



See here for more information: http://rmarkdown.rstudio.com/articles_docx.html

```{r cars}
summary(cars)
```

## Heading 2

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

### Heading 3

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

#### Heading 4



